\section*{Declarations}

\subsection*{Funding}

No specific funding was received for this work.

\subsection*{Conflicts of interest/Competing interests}

The authors declare that they have no competing interests.

\subsection*{Ethics approval and consent to participate}

Not applicable. This study used publicly available, de-identified molecular and clinical datasets.

\subsection*{Availability of data and material}

All datasets used in this study are publicly available. TCGA-BRCA, TCGA PanCancer Atlas cohorts, METABRIC, CPTAC 2020, and SMC 2018 molecular and clinical data were accessed through cBioPortal. GSE96058/SCAN-B data were accessed through the Gene Expression Omnibus and the associated public processed data package. Analysis scripts, compact processed result tables, figures, reports, and the manuscript source are available in the public GitHub repository: \url{https://github.com/123hzq321/cancer-multiomics-learning-models-benchmark}.

\subsection*{Code availability}

Analysis scripts used to download, preprocess, train, and evaluate the models are available at \url{https://github.com/123hzq321/cancer-multiomics-learning-models-benchmark}. Key scripts include:
\begingroup
\footnotesize
\begin{itemize}
\item \path{train_joined_metabric_small_liquid_external_validation.py}
\item \path{train_large_scale_mrna_baselines.py}
\item \path{train_multicancer_internal_benchmark.py}
\item \path{reviewer_cv_noise_significance_analysis.py}
\end{itemize}
\endgroup

\subsection*{Consent for publication}

Not applicable.

\subsection*{Authors' contributions}

Z.H. conceived the study, designed the computational experiments, processed the data, implemented the analysis pipeline, performed model training and evaluation, prepared figures and tables, and drafted the manuscript. X.B. supervised the study, contributed clinical interpretation, and revised the manuscript. Both authors reviewed and approved the final manuscript.

\subsection*{Acknowledgements}

Not applicable.
